Classification of Parkinson's disease patients using Bayesian deep learning based on fMRI data

### 2020-06-26 article.tex
Abstract size reduced to fit in the front page

\begin{abstract}
The goal of resting-state functional magnetic resonance imaging (fMRI) is to investigate the brain's functional connections by using the temporal similarity between blood oxygenation level-dependent (BOLD) signals in different regions of the brain “at rest” as an indicator of synchronous neural activity.
However having different images of patients' brains regardless of the sequential time-based information, may contain enough data to investigate their brains and enables us to recognize some diseases.
In this paper, we propose a novel method to automatically extract this non-time sequence-based information using a Bayesian deep learning algorithm based on a convolutional neural network (CNN).
Instead of using some predefined points of interest (POIs) we use the whole data in the training phase so those points of the brain which do not contain related information about the disease will be ignored automatically by the trained model.
Moreover, this method does not make any assumptions about the disease, patients, etc.,
makes it a possible universal disease diagnosis approach to differentiate diseases having an impact on brain functionality.
This method is a supervised algorithm with a small number of calculations using three-dimensional CNN.
Each fMRI scan (which contains {\it t} time slices of the brain) of patients will be divided into {\it t} different 3D images enabling us to make the dataset much bigger in number and calculations way simpler.
Subsequently, all of these images are fed to a Bayesian network similar to LeNet-5 (but in three dimensions) to train our model.
Then to determine if a person is suffering from Parkinson's or not, we test his/her {\it t} fMRI images and get {\it t} different results which leads to a fraction (probability) of how unhealthy his/her brain is and if that fraction is above 0.5 we can classify that sample as a Parkinson's patient. As a result, the proposed method would be able to distinguish Parkinson's disease patients from healthy controls accurately. Experimental results confirm the efficiency of the proposed method and its outperformance.
\end{abstract}

>>>>

\begin{abstract}
The goal of resting-state fMRI is to investigate the brain's functional connections in different regions of the brain as an indicator of synchronous neural activity.
However having different images of patients' brains regardless of the sequential time-based information, may contain enough data to investigate their brains.
In this paper, we propose a novel method to automatically extract this non-time sequence-based information using a Bayesian deep learning algorithm based on a convolutional neural network (CNN).
Instead of using some predefined points of interest (POIs), we use the whole data in the training phase so those points of the brain which do not contain related information about the disease will be ignored automatically by the trained model.
Moreover, this method does not make any assumptions about the disease, patients, etc.,
makes it a possible universal disease diagnosis approach to differentiate diseases having an impact on brain's functionality.
Each fMRI scan of patients will be divided into {\it t} different 3D images enabling us to make the dataset much bigger in number and calculations way simpler.
All of these images are fed to a Bayesian network to train our model.
Then to determine if a person is a patient, we test {\it t} fMRI slices and get {\it t} different results which leads to a fraction (probability) of how unhealthy the brain is. Experimental results confirm the efficiency of the method and its outperformance.
\end{abstract}
